Insert the article title here

### 2020-07-25 tex/results.tex
more edits in results

We performed a grid-independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
constant electric field aligned with the $z$-axis (a similar setup to the square cylinder on Fig. 18 of 
Rockstuhl et al.\cite{rockstuhl2005}). 
Due to the nature of the geometry and its sharp edges, it was challenging to see proper convergence. However,
for this type of physics, convergence has been studied in our previous work \cite{ClementiETal2019}. (NOT SURE IF WE NEED TO MENTION THIS)
Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 
triangles (density $1.11\times10^-4$ $N/\text{\AA}$) to 19,200 (density $9.05\times10^-5$ $N/\text{\AA}$) 
triangles: the computed results show no discernible difference.

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{cubeL535nm_15Kvs19K.pdf} 
    \caption{Grid-independence study for a SiC cube of side $L=535 nm$ submerged in air under a constant 
    electric field in the $z$-direction. The curves represent the extinction cross-section divided by $L^2$ 
    as a function of wavelength divided by $L$.}
    \label{fig:cube535}
 \end{figure}

@@

Based on the results of the grid independence study we decided to use the densities in the order of $6-9e^-5$
to produce the meshes for the replication of figures 14a and 14b on Rockstuhl's work (case a1=672, b=328). For the third 
dimension we needed to chose a value that represents "infinity". To achieve this, we study the effects of 
elongation on the third dimension. In Figure \ref{fig:ext_y_14} we present the results for two different
values of the third dimension, $y=1344$ nm (2xa) and $y=2688$ nm (4xa). We see that as we extend $y$ the 
intensity of some peaks decreases, this is because some of the peaks are related to this component. Therefore, 
from now on we use $y=2688$ nm. It is worth noting that we could have increased this value more, however, the
simulations will become computational more expensive and we will still have the effects of having a 3D model.

@@

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.45\textwidth]{ext_y_14a.pdf}}
    \subfloat{\includegraphics[width=0.45\textwidth]{ext_y_14b.pdf}} 
    \caption{Effect of the elongation of the third direction ($y$) on the 
        extinction cross section of a rectangular prism of SiC of dimensions $a=672$ nm 
        and $b=328$ nm, submerged in air and under a constant electric field 
        parallel to the z-axis. The left plot corresponds to a configuration such that the electric 
        field is parallel to $b$ (configuration (A) on Figure \ref{fig:rectangle_sketch}), while the 
        right plot corresponds to a configuration such that the electric field is 
        parallel to $a$ (configuration (B) on Figure \ref{fig:rectangle_sketch}}
    \label{fig:ext_y_14}   
 \end{figure}

To generate the meshes for these simulations, we initially used the open source software Trimesh 
(\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
uniform mesh and that it was not possible to produce regular triangles with the functions 
available when having a prism. To overcome this, we created our own mesh using python scripts,
and create uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
of rounding the edges. We wanted to round the edges since in Rockstuhl work this was mentioned 
as a factor that introduces extra peaks on the response. We were not able to control the 
roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
decided to use the default settings on Trimesh. Figure \ref{fig:tri_reg_round_14} shows the 
results on the effect of uniformity and roundness. You can see that the second peak is not
present in the green curve, which can be attributed to the effect of the roundness. This is 
consistent with the results on Rockstuhl's work.

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.45\textwidth]{tri_reg_round_14a.pdf}}
    \subfloat{\includegraphics[width=0.45\textwidth]{tri_reg_round_14b.pdf}}
    \caption{ Effect of uniformity and roundness on the mesh on the 
    extinction cross section of a rectangular prism of SiC of dimensions $a=672$ nm, 
    $b=328$ nm and $y=2688$ nm, submerged in air and under a constant electric field 
    parallel to the z-axis}
    \label{fig:tri_reg_round_14}
 \end{figure}

Once we have found the "best" possible geometry approximation, we show how our results 
(green curve in Figure \ref{fig:tri_reg_round_14}) compare 
with the original results from Rockstuhl's Figure 14. We have obtained Rockstuhl's curves by using 
the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
presented in Figure \ref{fig:rep_14}. We can say that the main peaks presented in Rockstuhl et al. are 
successfully replicated. While we still have the presence of a third peak in our results, we believe 
this is a consequence of the 3D nature of our geometry.

 \begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.45\textwidth]{replication_14a.pdf}}
    \subfloat{\includegraphics[width=0.45\textwidth]{replication_14b.pdf}} 
    \caption{Replication of Figure 14 from Rockstuhl 2005. Extinction cross section of a
    rectangular prism of SiC of dimensions $a=672$ nm, $b=328$ nm and $y=2688$ nm, submerged
    in air and under a constant electric field parallel to the z-axis.}
    \label{fig:rep_14}
 \end{figure}

>>>>

We performed a grid-independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
constant electric field aligned with the $z$-axis (a similar setup to the square cylinder on Fig. 18 of 
Rockstuhl et al.\cite{rockstuhl2005}). 
Due to the nature of the geometry and its sharp edges, it was challenging to see proper convergence. However,
for this type of physics, convergence has been studied in our previous work \cite{ClementiETal2019}. (NOT SURE IF WE NEED TO MENTION THIS)
Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 
triangles (density $1.11\times10^{-4}$ $N/\text{\AA}$) to 19,200 (density $9.05\times10^{-5}$ $N/\text{\AA}$) 
triangles: the computed results show no discernible difference.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{cubeL535nm_15Kvs19K.pdf} 
    \caption{Grid-independence study for a SiC cube of side $L=535 nm$ submerged in air under a constant 
    electric field in the $z$-direction. The curves represent the extinction cross-section divided by $L^2$ 
    as a function of wavelength divided by $L$.}
    \label{fig:cube535}
 \end{figure}

@@

Based on the results of our grid-independence study, we decided to use triangle densities in the order of $6$ to $9\times10^{-5}$
to produce the meshes for the replication of figures 14a and 14b in the work of Rockstuhl et al.\ (case $a1=672$, $b=328$). For the third 
dimension, we needed to choose a value that represents ``infinity.'' To achieve this, we studied the effects of 
elongating the cylinder to the third dimension. In Figure \ref{fig:ext_y_14}, we present the results for two different
values of the length in the third dimension, $y=1344$ nm ($2\times a$) and $y=2688$ nm ($4\times a$). We see that as we make $y$ longer, the 
intensity of some peaks decreases, due to the fact that some of the peaks are associated to this component. Therefore, 
from now on we use $y=2688$ nm. We could have increased this value more, but the
simulations then become computationally more expensive and we would still have the 3D effects in the model.

@@

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.48\textwidth]{ext_y_14a.pdf}}
    \subfloat{\includegraphics[width=0.48\textwidth]{ext_y_14b.pdf}} 
    \caption{Effect of the elongation of the third direction ($y$) on the 
        extinction cross section of a rectangular prism of SiC of dimensions $a=672$ nm 
        and $b=328$ nm, submerged in air and under a constant electric field 
        parallel to the z-axis. The left plot corresponds to a configuration such that the electric 
        field is parallel to $b$ (configuration (A) on Figure \ref{fig:rectangle_sketch}), while the 
        right plot corresponds to a configuration such that the electric field is 
        parallel to $a$ (configuration (B) on Figure \ref{fig:rectangle_sketch}}
    \label{fig:ext_y_14}   
 \end{figure}

To generate the meshes for these simulations, we initially used the open source software Trimesh 
(\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
uniform mesh and that it was not possible to obtain regular triangles with the functions 
available when having a prism. To overcome this, we created our own mesh using Python scripts,
and obtained uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
of rounding the edges---Rockstuhl et al.\ mentioned rounded edges
as a factor that introduces extra peaks on the response. We were unable to control the 
roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
decided to use the default settings on Trimesh. Figure \ref{fig:tri_reg_round_14} shows the 
results of the effect of uniformity and roundness. One can see that the second peak is not
present in the green curve, which can be attributed to the effect of the roundness. This is 
consistent with the results in Rockstuhl et al.

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.48\textwidth]{tri_reg_round_14a.pdf}}
    \subfloat{\includegraphics[width=0.48\textwidth]{tri_reg_round_14b.pdf}}
    \caption{ Effect of uniformity and roundness on the mesh on the 
    extinction cross section of a rectangular prism of SiC of dimensions $a=672$ nm, 
    $b=328$ nm and $y=2688$ nm, submerged in air and under a constant electric field 
    parallel to the z-axis}
    \label{fig:tri_reg_round_14}
 \end{figure}

Once we have found the ``best'' possible geometry construction, we show how our results 
(green curve in Figure \ref{fig:tri_reg_round_14}) compare 
with the original results from Rockstuhl's Figure 14. We have obtained Rockstuhl's curves by using 
the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
presented in Figure \ref{fig:rep_14}: the main peaks presented in Rockstuhl et al.\ are 
successfully replicated. While we still have the presence of a third peak in our results, we conjecture 
that this is a consequence of the 3D effects in our geometry.

 \begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14a.pdf}}
    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14b.pdf}} 
    \caption{Replication of Figure 14 from Rockstuhl 2005. Extinction cross section of a
    rectangular prism of SiC of dimensions $a=672$ nm, $b=328$ nm and $y=2688$ nm, submerged
    in air and under a constant electric field parallel to the z-axis.}
    \label{fig:rep_14}
 \end{figure}
